Manuscript Figures

### 2018-06-07 Manuscript Figures.Rmd
Add protein dominance to chromosome plot
And also clean up code and move load/clean functions to proper scripts.  Remove Maggie subgenomes and Orphan Genes lists

```{r chromosome_plot, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=8, fig.height=6}
v4_subg_jw <-
  subgenome %>%
  left_join(positions, by=c("gene2"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, subgenome) %>%
  rename(Subgenome=subgenome) %>%
  subset(Subgenome %in% c("sub1", "sub2"))

v4_dom_jw <- expressedPairs
v4_dom_jw$Subgenome <- "no dominance"
v4_dom_jw$Subgenome[v4_dom_jw$FPKM_mean1 / v4_dom_jw$FPKM_mean2 > 2] <- "dom"
v4_dom_jw$Subgenome[v4_dom_jw$FPKM_mean2 / v4_dom_jw$FPKM_mean1 > 2] <- "dom"
v4_dom_jw$Maize1[v4_dom_jw$FPKM_mean2 / v4_dom_jw$FPKM_mean1 > 2] <- v4_dom_jw$Maize2[v4_dom_jw$FPKM_mean2 / v4_dom_jw$FPKM_mean1 > 2]
df0 <- v4_dom_jw[v4_dom_jw$Subgenome %in% c("no dominance"),]
df0$Maize1 <- df0$Maize2
v4_dom_jw <- bind_rows(v4_dom_jw, df0)
v4_dom_jw <-
  v4_dom_jw %>%
  select(Maize1, Subgenome) %>%
  left_join(positions, by=c("Maize1"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, Subgenome)

## 6,773 - 3,875 (no map) -~-  1,018 (no positions); split/merge is fine = 1,896 orphan v4_ids with positions based on Zea_mays.AGPv4.36.chr.gff3
v4_orph_jw <-
  OrphanGenes %>%
  select(gene) %>%
  left_join(maize.genes.v3_to_v4.map, c("gene" = "v3_id"))
v4_orph_na <- v4_orph_jw[is.na(v4_orph_jw$v4_id),]
v4_orph_jw <- v4_orph_jw[!is.na(v4_orph_jw$v4_id),]
v4_orph_jw <-
  v4_orph_jw %>%
  select(v4_id) %>%
  left_join(positions, by=c("v4_id"="geneID"))
v4_orph_jw <- v4_orph_jw[!is.na(v4_orph_jw$Pos_end),]
v4_orph_jw$Subgenome <- "orphan"
v4_orph_jw <-
  v4_orph_jw %>%
  select(Chromosome, Pos_start, Pos_end, Subgenome)

centromere.v4.positions <-
  centromere.v4.positions %>%
  rename(Chromosome="X__1", Pos_start="X__6", Pos_end="X__7") %>%
  select(Chromosome, Pos_start, Pos_end)
centromere.v4.positions

df1 <- centromere.v4.positions
df1$x <- -.45
df1$xend <- .45
df2 <- v4_subg_jw
df2$x <- -.45
df2$xend <- -.05
df3 <- v4_dom_jw
df3$x <- .05
df3$xend <- .45
segment_data <- bind_rows(df2,df3)
segment_data <- segment_data[!is.na(segment_data$Pos_start),]
segment_data <-
  segment_data %>%
  ungroup()
segment_data$Subgenome[segment_data$Subgenome %in% c("sub1")] <- "Maize1"
segment_data$Subgenome[segment_data$Subgenome %in% c("sub2")] <- "Maize2"
# segment_data$Subgenome[segment_data$Subgenome %in% c("dom")] <- "Dominant Homeolog"
segment_data <- segment_data %>% subset(Subgenome %in% c("Maize1", "Maize2", "orphan", "sub1dom", "sub2dom", "dom"))
centromere_data <- df1

#--------------------------------------------------------------------------------------------------#
## Make the plot
chromosome_plot <-
  ggplot(data=v4) +
    geom_bar(aes(v4$chromosome, v4$size), stat="identity", fill="grey70") +
    # geom_segment(data=segment_data, aes(x=Chromosome+x, xend=Chromosome+xend, y=Pos_start, yend=Pos_end, colour=Subgenome), size=.001) +
    geom_rect(data=segment_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end, color=Subgenome, fill=Subgenome)) +
    geom_rect(data=centromere_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end)) +
    scale_fill_manual(values=c("green", "red", "blue", "black")) +
    scale_color_manual(values=c("green", "red", "blue", "black")) +
    scale_x_discrete(limits=c("Chr1","Chr2","Chr3","Chr4","Chr5","Chr6","Chr7","Chr8","Chr9","Chr10")) +
    scale_y_continuous(labels=format_si())
chromosome_plot  +
  labs(
  # title="Subgenome Locations by Chromosome",
  x="Chromosome",
  y="Position on Chromosome"
)

@@

# Remove pollen
data <-
  data %>%
  subset(!sample %in% c("B73 Mature Pollen"))

@@

```{r print, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
ggsave("Output/Figure 1.png", plot = chromosome_plot)

png("Output/Figure 2a.png");
grid.draw(GOTerms_by_subgenome_a)
dev.off()
png("Output/Figure 2b.png");
grid.draw(GOTerms_by_subgenome_b)
dev.off()

ggsave("Output/Figure 3.png", plot = subgenome_isoforms_scatter)
ggsave("Output/Figure 4.png", plot = subgenome_expression_scatter_rep)
ggsave("Output/Figure 5.png", plot = subgenome_protein_scatter_rep)
ggsave("Output/Figure 6.png", plot = subgenome_expression_protein_foldchange_scatter)
ggsave("Output/Figure 7.png", plot = subgenome_expression_protein_scatter)
ggsave("Output/Figure 8.png", plot = subgenome_expression_protein_scatter_rep)
ggsave("Output/Figure S1.png", plot = subgenome_expression_scatter)
ggsave("Output/Figure S2.png", plot = subgenome_protein_scatter)
ggsave("Output/Figure S3.png", plot = subgenome_expression_protein_scatter)
```

>>>>

```{r chromosome_plot_exp, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=8, fig.height=6}
subgenome.positions <-
  subgenome %>%
  left_join(B73.v4.gene.positions, by=c("gene2"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, subgenome) %>%
  rename(Subgenome=subgenome) %>%
  subset(Subgenome %in% c("sub1", "sub2"))

dominant_homeolog_exp <- expressedPairs
dominant_homeolog_exp$Subgenome <- "no dominance"
dominant_homeolog_exp$Subgenome[dominant_homeolog_exp$FPKM_mean1 / dominant_homeolog_exp$FPKM_mean2 > 2] <- "Dominant Expression"
dominant_homeolog_exp$Subgenome[dominant_homeolog_exp$FPKM_mean2 / dominant_homeolog_exp$FPKM_mean1 > 2] <- "Dominant Expression"
dominant_homeolog_exp$Maize1[dominant_homeolog_exp$FPKM_mean2 / dominant_homeolog_exp$FPKM_mean1 > 2] <- dominant_homeolog_exp$Maize2[dominant_homeolog_exp$FPKM_mean2 / dominant_homeolog_exp$FPKM_mean1 > 2]
df0 <- dominant_homeolog_exp[dominant_homeolog_exp$Subgenome %in% c("no dominance"),]
df0$Maize1 <- df0$Maize2
dominant_homeolog_exp <- bind_rows(dominant_homeolog_exp, df0)
dominant_homeolog_exp <-
  dominant_homeolog_exp %>%
  select(Maize1, Subgenome) %>%
  left_join(B73.v4.gene.positions, by=c("Maize1"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, Subgenome)

df1 <- B73.v4.centromere.positions
df1$x <- -.45
df1$xend <- .45
df2 <- subgenome.positions
df2$x <- -.45
df2$xend <- -.05
df3 <- dominant_homeolog_exp
df3$x <- .05
df3$xend <- .45
segment_data <- bind_rows(df2,df3)
segment_data <- segment_data[!is.na(segment_data$Pos_start),]
segment_data <-
  segment_data %>%
  ungroup()
segment_data$Subgenome[segment_data$Subgenome %in% c("sub1")] <- "Maize1"
segment_data$Subgenome[segment_data$Subgenome %in% c("sub2")] <- "Maize2"
# segment_data$Subgenome[segment_data$Subgenome %in% c("dom")] <- "Dominant Homeolog"
segment_data <- segment_data %>% subset(Subgenome %in% c("Maize1", "Maize2", "Dominant Expression"))
centromere_data <- df1

## Make the plot
chromosome_plot_exp <-
  ggplot(data=B73.v4.chr.size) +
  geom_bar(aes(B73.v4.chr.size$chromosome, B73.v4.chr.size$size), stat="identity", fill="grey70") +
  # geom_segment(data=segment_data, aes(x=Chromosome+x, xend=Chromosome+xend, y=Pos_start, yend=Pos_end, colour=Subgenome), size=.001) +
  geom_rect(data=segment_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end, color=Subgenome, fill=Subgenome)) +
  geom_rect(data=centromere_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end)) +
  scale_fill_manual(values=c("green", "red", "blue", "black")) +
  scale_color_manual(values=c("green", "red", "blue", "black")) +
  scale_x_discrete(limits=c("Chr1","Chr2","Chr3","Chr4","Chr5","Chr6","Chr7","Chr8","Chr9","Chr10")) +
  scale_y_continuous(labels=format_si())
chromosome_plot_exp  +
  labs(
    # title="Subgenome Locations by Chromosome",
    x="Chromosome",
    y="Position on Chromosome"
  )
```

```{r chromosome_plot_abundance, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=8, fig.height=6}
subgenome.positions <-
  subgenome %>%
  left_join(B73.v4.gene.positions, by=c("gene2"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, subgenome) %>%
  rename(Subgenome=subgenome) %>%
  subset(Subgenome %in% c("sub1", "sub2"))

dominant_homeolog_abun <- expressedProteinsPairs
dominant_homeolog_abun$Subgenome <- "no dominance"
dominant_homeolog_abun$Subgenome[dominant_homeolog_abun$dNSAF_mean1 / dominant_homeolog_abun$dNSAF_mean2 > 2] <- "Dominant Abundance"
dominant_homeolog_abun$Subgenome[dominant_homeolog_abun$dNSAF_mean2 / dominant_homeolog_abun$dNSAF_mean1 > 2] <- "Dominant Abundance"
dominant_homeolog_abun$Maize1[dominant_homeolog_abun$dNSAF_mean2 / dominant_homeolog_abun$dNSAF_mean1 > 2] <- dominant_homeolog_abun$Maize2[dominant_homeolog_abun$dNSAF_mean2 / dominant_homeolog_abun$dNSAF_mean1 > 2]
df0 <- dominant_homeolog_abun[dominant_homeolog_abun$Subgenome %in% c("no dominance"),]
df0$Maize1 <- df0$Maize2
dominant_homeolog_abun <- bind_rows(dominant_homeolog_abun, df0)
dominant_homeolog_abun <-
  dominant_homeolog_abun %>%
  select(Maize1, Subgenome) %>%
  left_join(B73.v4.gene.positions, by=c("Maize1"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, Subgenome)

df1 <- B73.v4.centromere.positions
df1$x <- -.45
df1$xend <- .45
df2 <- subgenome.positions
df2$x <- -.45
df2$xend <- -.05
df3 <- dominant_homeolog_abun
df3$x <- .05
df3$xend <- .45
segment_data <- bind_rows(df2,df3)
segment_data <- segment_data[!is.na(segment_data$Pos_start),]
segment_data <-
  segment_data %>%
  ungroup()
segment_data$Subgenome[segment_data$Subgenome %in% c("sub1")] <- "Maize1"
segment_data$Subgenome[segment_data$Subgenome %in% c("sub2")] <- "Maize2"
# segment_data$Subgenome[segment_data$Subgenome %in% c("dom")] <- "Dominant Homeolog"
segment_data <- segment_data %>% subset(Subgenome %in% c("Maize1", "Maize2", "Dominant Abundance"))
centromere_data <- df1

## Make the plot
chromosome_plot_abundance <-
  ggplot(data=B73.v4.chr.size) +
  geom_bar(aes(B73.v4.chr.size$chromosome, B73.v4.chr.size$size), stat="identity", fill="grey70") +
  # geom_segment(data=segment_data, aes(x=Chromosome+x, xend=Chromosome+xend, y=Pos_start, yend=Pos_end, colour=Subgenome), size=.001) +
  geom_rect(data=segment_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end, color=Subgenome, fill=Subgenome)) +
  geom_rect(data=centromere_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end)) +
  scale_fill_manual(values=c("green", "red", "blue", "black")) +
  scale_color_manual(values=c("green", "red", "blue", "black")) +
  scale_x_discrete(limits=c("Chr1","Chr2","Chr3","Chr4","Chr5","Chr6","Chr7","Chr8","Chr9","Chr10")) +
  scale_y_continuous(labels=format_si())
chromosome_plot_abundance  +
  labs(
    # title="Subgenome Locations by Chromosome",
    x="Chromosome",
    y="Position on Chromosome"
  )
```

@@

# # Remove pollen
# data <-
#   data %>%
#   subset(!sample %in% c("B73 Mature Pollen"))

@@

```{r print, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
# ggsave("Output/Figure 1a.png", plot = chromosome_plot_exp)
# ggsave("Output/Figure 1b.png", plot = chromosome_plot_abundance)
# 
# png("Output/Figure 2a.png");
# grid.draw(GOTerms_by_subgenome_a)
# dev.off()
# png("Output/Figure 2b.png");
# grid.draw(GOTerms_by_subgenome_b)
# dev.off()
# 
# ggsave("Output/Figure 3.png", plot = subgenome_isoforms_scatter)
# ggsave("Output/Figure 4.png", plot = subgenome_expression_scatter_rep)
# ggsave("Output/Figure 5.png", plot = subgenome_protein_scatter_rep)
# ggsave("Output/Figure 6.png", plot = subgenome_expression_protein_foldchange_scatter)
# ggsave("Output/Figure 7.png", plot = subgenome_expression_protein_scatter)
# ggsave("Output/Figure 8.png", plot = subgenome_expression_protein_scatter_rep)
# ggsave("Output/Figure S1.png", plot = subgenome_expression_scatter)
# ggsave("Output/Figure S2.png", plot = subgenome_protein_scatter)
# ggsave("Output/Figure S3.png", plot = subgenome_expression_protein_scatter)
```
